A Continual Planner that Switches Between Serial and Decision-Theoretic Planning

### 2010-11-17 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Equation fix.
 - Charles

\begin{equation}\label{eq:evaluation}
V_\node(\state) = \sum_{\action \in \actions}
\selection_\node(\action) \reward(\state, \action) + \beta \sum_{\action, \observation,
\state', \node'} \transition_\node(\action, \observation, \node')
\transProb(\state, \action, \state') \obsDist_\observ(\state',
\action) V_{\node'}(\state')
\end{equation}

@@

@@

the effects of a sensing schema are perceptual, whereas the effects of
an operator schema are on the underlying state space.

>>>>

\begin{equation}\label{eq:evaluation}
\begin{array}{lcl}
V_\node(\state) & = & \sum_{\action \in \actions}
\selection_\node(\action) \reward(\state, \action) \;\; + \vspace{1ex} \\

&& \hspace{-10ex} \beta \sum_{\action, \observation,
\state', \node'} \transition_\node(\action, \observation, \node')
\transProb(\state, \action, \state') \obsDist_\observ(\state',
\action) V_{\node'}(\state')
\end{array}
\end{equation}

@@

Goal expressions in the problem description ---for example
$(\pp{kval}~(\pp{location}~\pp{cornflakes}))$ expresses ``the robot
knows where the {\em cornflakes}--- are treated as control-knowledge
by the planner. Here, a plan is not considered valid unless in the
finial stet the goal condition is satisfied.

@@

The modelling language of choice for planning in probabilistic
problems is the Probabilistic Planning Domain Definition
Language~\cite{younes:littman:04}. PPDDL was used in all 3 of the
International Planning Competitions since 2004. A variation on PDDL
for describing domains with stochastic actions and uncertain starting
configurations, PPDDL is a declarative first-order (a.k.a.,
relational) that facilitates factored description of domains and
problem instances. There are straightforward compilations from
problems expressed compactly in PPDDL to propositional representations
amenable to state-of-the-art planning procedures.  Because this
language cannot model domains that feature partial observability, for
our setting we have developed DTPDDL, an extension of PPDDL to partial
observability.

For example, $(:\pp{predicates} (\pp{location} ?p - VisualObject))$
says that there is a unary predicate

the effects of a {\em sense} schema are perceptual, whereas the
effects of an {\em operator} schema are over state propositions.
